Supplementary Materials: Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus

### 2023-12-19 supplementary_thev_trxptome.Rmd
wrote some E2 reg results and added gels designed primers for E2 trxpt_15 and pol

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
library(knitr)
library(tidyverse)
library(gt)

source("scripts/r/bam_file_analysis.R")
```

@@

```{r Sup Table 1C}
gt(tp_reg_expr_72)
```

>>>>

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
library(knitr)
library(tidyverse)
library(flextable)
source("scripts/r/bam_file_analysis.R")
source("scripts/r/reg_by_reg_plots.R")
```

@@

```{r Sup Table 1C}
flextable(tp_reg_expr_72) %>% theme_zebra()
```

\newpage
## Supplementary PCR Methods
```{r Supplementary PCR Methods}
set_flextable_defaults(font.size = 3.5)

flextable(supp_pcr_meth_tab) %>%
  theme_zebra() %>%
  flextable::fontsize(j = c("forwardP", "reverseP"), size = 3) %>%
  flextable::align(align = "center", part = "all") %>%
  flextable::width(., width = 0.35) %>% 
  colformat_image(j = "gel_image", i = c(1, 3:7, 9, 10), na_str = "-",
                  width = 1, height = 1) %>%
  flextable::width(j = ~forwardP, width = 1) %>%
  flextable::width(j = ~reverseP, width = 1) %>%
  # flextable::width(j = ~valid_status, width = 0.35) %>%
  flextable::width(j = ~gel_image, width = 1) %>% 
  footnote(., i = c(1:6, 7, 9, 10), j = 12, value = as_paragraph(c("Primer binds exon 1")),
           ref_symbols = c("a"), part = "body") %>%
  footnote(., i = c(1:6, 7, 9, 10), j = 13, value = as_paragraph(c("Primer binds terminal exon")),
           ref_symbols = c("b"), part = "body")
```
